---
title: "Final Project"
author: "Madeline Ness"
date: "4/25/2018"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###Import Data
```{r, include = FALSE}
setwd("/Users/Madeline/Desktop/DA_101/Final")

FAO = read.csv("FAO.csv")
WPop = read.csv("World_Pop.csv")
```

```{r, include = FALSE}
library(dplyr)
library(ggplot2)
library(xtable)
library(knitr)
library(car)
library(leaps)
library(MASS)
library(Hmisc)
library(reshape2)
```

```{r}
#CLEANIG UP DATA FOOD PRODUCTION

FAO_1 <- FAO[c(3, 5, 7, 8, 11:63)]

#Viewing list of variables in Area column to see what needs to be changed 
#levels(FAO_1$Area)
```

```{r}
#Melt
FAO_2 <- melt(FAO_1, id=c("Area", "Item", "Element", "Unit"))
```

```{r}
#Rename columns
colnames(FAO_2)[colnames(FAO_2)=="variable"] <- "Year"
colnames(FAO_2)[colnames(FAO_2)=="value"] <- "Production"
```

```{r}
#Fix Counties by renaming them 
FAO_2$Area <- sub("Bolivia (Plurinational State of)","Bolivia", FAO_2$Area)
FAO_2$Area <- sub("China, Hong Kong SAR","Hong Kong SAR, China", FAO_2$Area)
FAO_2$Area <- sub("China, Macao SAR","Macao SAR, China", FAO_2$Area)
FAO_2$Area <- sub("China, mainland","China", FAO_2$Area)
FAO_2$Area <- sub("C\xf4te d'Ivoire","Cote d’Ivoire", FAO_2$Area)
FAO_2$Area <- sub("Czechia","Czech Republic", FAO_2$Area)
FAO_2$Area <- sub("Democratic People's Republic of Korea","Korea, Dem. People’s Rep.", FAO_2$Area)
FAO_2$Area <- sub("Iran (Islamic Republic of)","Iran, Islamic Rep.", FAO_2$Area)
FAO_2$Area <- sub("Lao People's Democratic Republic","Lao PDR", FAO_2$Area)
FAO_2$Area <- sub("Republic of Korea","Korea, Rep.", FAO_2$Area)
FAO_2$Area <- sub("Republic of Moldova","Moldova", FAO_2$Area)
FAO_2$Area <- sub("Saint Kitts and Nevis","St. Kitts and Nevis", FAO_2$Area)
FAO_2$Area <- sub("Saint Lucia","St. Lucia", FAO_2$Area)
FAO_2$Area <- sub("Saint Vincent and the Grenadines","St. Vincent and the Grenadines", FAO_2$Area)
FAO_2$Area <- sub("The former Yugoslav Republic of Macedonia","Macedonia, FYR", FAO_2$Area)
FAO_2$Area <- sub("United Republic of Tanzania","Tanzania", FAO_2$Area)
FAO_2$Area <- sub("United States of America","United States", FAO_2$Area)
FAO_2$Area <- sub("Venezuela (Bolivarian Republic of)","Venezuela, RB", FAO_2$Area)
FAO_2$Area <- sub("Viet Nam","Vietnam", FAO_2$Area)
```

```{r}
#Delete Taiwan (no population)
FAO_3 <- FAO_2 %>%
  filter(Area != "China, Taiwan Province of")
```

```{r}
#fix year
FAO_3$Year <- sub("Y","", FAO_3$Year)
```

```{r}
# Clean up WPop like FAO
WPop_1 <- WPop[c(1, 5:57)]
```

```{r}
#Checking the number of countries
#levels(WPop_1$Country.Name)
```

```{r}
#Melt
WPop_2 <- melt(WPop_1, id=c("Country.Name"))
```

```{r}
#Rename columns
colnames(WPop_2)[colnames(WPop_2)=="Country.Name"] <- "Area"
colnames(WPop_2)[colnames(WPop_2)=="variable"] <- "Year"
colnames(WPop_2)[colnames(WPop_2)=="value"] <- "Population"
```

```{r}
#FIX Year
WPop_2$Year <- sub("X","", WPop_2$Year)
WPop_2$Year <- sub("..YR\\d\\d\\d\\d.","", WPop_2$Year)
```

```{r}
# Fix country names
WPop_2$Area <- sub("Bahamas, The","Bahamas", WPop_2$Area)
WPop_2$Area <- sub("Gambia, The","Gambia", WPop_2$Area)
WPop_2$Area <- sub("Kyrgyz Republic","Kyrgyzstan", WPop_2$Area)
WPop_2$Area <- sub("Congo, Rep.","Congo", WPop_2$Area)
WPop_2$Area <- sub("Yemen, Rep.","Yemen", WPop_2$Area)
WPop_2$Area <- sub("Egypt, Arab Rep.","Egypt", WPop_2$Area)
WPop_2$Area <- sub("Slovak Republic","Slovakia", WPop_2$Area)
```

```{r}
#Remove rows from WPop that aren't in FAO and merge
#Create full dataset with all variables from FAO_3
POP_PRO <- left_join(FAO_3, WPop_2)
POP_PRO$Year <- as.numeric(POP_PRO$Year)
```

```{r}
#Remove data not being used
rm(FAO, FAO_1, FAO_2, FAO_3, WPop, WPop_1, WPop_2)
```

```{r}
#Find largest producing countries

Pop_Pro_3 <- POP_PRO %>%
  group_by(Area, Year, Element) %>%
  summarise(ProByPop = sum(Production/Population), Avg_Production_year = sum(Production)/52, 
            Tot_Pro = sum(Production), Avg_Pop = sum(Population)/52)

```


### 8 Countries all items
```{r}
Pop_Pro_AI <- POP_PRO[which(POP_PRO$Area  == "Nigeria" | POP_PRO$Area  == "China" | 
                            POP_PRO$Area  == "United States" | POP_PRO$Area  == "India" | 
                            POP_PRO$Area  == "Germany" | POP_PRO$Area  == "Brazil" |
                            POP_PRO$Area  == "Denmark" | POP_PRO$Area  == "Canada"),]

Pop_Pro_AI_2 <- Pop_Pro_AI %>%
  group_by(Area, Year, Element, Item)%>%
  summarise(ProByPop = sum(Production/Population), Avg_Production_year = sum(Production)/52)
```

```{r}
Pop_Pro_AI_2 %>%
  group_by(Area)%>%
  ggplot(aes(x = Year, y = ProByPop, colour = Area)) +
  stat_summary(fun.y = "mean", geom = "line", size = 1) +
  scale_x_continuous(breaks=seq(1961, 2013, 10)) +
  facet_wrap(~Element) +
  labs(x = "Year", y = "Amount Produced by Population", 
       title = "Element of Production of Population by Country") +
  theme(text = element_text(size=17), axis.text.x = element_text(angle=90, hjust=1))
```
```{r}
Pop_Pro_AI_3 <- Pop_Pro_AI %>%
  group_by(Area, Year)%>%
  mutate(ProByPop = sum(Production, na.rm=T)/sum(Population, na.rm=T), Avg_Production_year = sum(Production)/52)

Pop_Pro_AI_3 %>%
  group_by(Area)%>%
  ggplot(aes(x = Year, y = ProByPop)) +
  geom_line(aes(x=Year, y=ProByPop, colour = Area), size = 1) + 
  scale_x_continuous(breaks=seq(1961, 2013, 10)) +
  labs(x = "Year", y = "Amount Produced by Population", 
       title = "Production by Population by Year ") +
  theme(text = element_text(size=17), axis.text.x = element_text(angle=90, hjust=1))
```
### 8 items all Countries 
```{r}
Pop_Pro_AC <- POP_PRO[which(POP_PRO$Item == "Cereals - Excluding Beer" | 
                            POP_PRO$Item == "Milk - Excluding Butter" |
                            POP_PRO$Item == "Vegetables" | 
                            POP_PRO$Item == "Starchy Roots" | 
                            POP_PRO$Item == "Maize and products" | 
                            POP_PRO$Item == "Sweet potatoes" | 
                            POP_PRO$Item == "Fruits - Excluding Wine" | 
                            POP_PRO$Item == "Rice (Milled Equivalent)"),]

Pop_Pro_AC_2 <- Pop_Pro_AC %>%
  group_by(Area, Year, Element, Item)%>%
  summarise(ProByPop = sum(Production/Population), Avg_Production_year = sum(Production)/52)
```

```{r}
Pop_Pro_AC_2 %>%
  group_by(Item)%>%
  ggplot(aes(x = Year, y = ProByPop, colour = Item)) +
  stat_summary(fun.y = "mean", geom = "line", size = 1) +
  scale_x_continuous(breaks=seq(1961, 2013, 10)) +
  facet_wrap(~Element) +
  labs(x = "Year", y = "Amount Produced by Population", 
       title = "Element of Production of Population by Item") +
  theme(text = element_text(size=17), axis.text.x = element_text(angle=90, hjust=1))
```
```{r}
Pop_Pro_AC_4 <- Pop_Pro_AC %>%
  group_by(Item, Year)%>%
  mutate(ProByPop_Item = sum(Production, na.rm=T)/sum(Population, na.rm=T), Avg_Production_year_item = sum(Production)/52)

Pop_Pro_AC_4 %>%
  group_by(Area)%>%
  ggplot(aes(x = Year, y = ProByPop_Item, color = Item)) +
  stat_summary(fun.y = "mean", geom = "line", size = 1) + 
  scale_x_continuous(breaks=seq(1961, 2013, 10)) +
  labs(x = "Year", y = "Item Production", 
       title = "Item Production per Year by Population") +
  theme(text = element_text(size=17), axis.text.x = element_text(angle=90, hjust=1)) 

```
###All items All Countries
```{r}
str(POP_PRO)
```

#The 8 and 8 Mainly for graphs
```{r}
Pop_Pro_A8 <- POP_PRO[which(POP_PRO$Item == "Cereals - Excluding Beer" | 
                              POP_PRO$Item == "Milk - Excluding Butter" |
                            POP_PRO$Item == "Vegetables" | 
                              POP_PRO$Item == "Starchy Roots" | 
                            POP_PRO$Item == "Maize and products" | 
                              POP_PRO$Item == "Sweet potatoes" | 
                            POP_PRO$Item == "Fruits - Excluding Wine" | 
                              POP_PRO$Item == "Rice (Milled Equivalent)"),]

Pop_Pro_A8 <- Pop_Pro_A8[which(Pop_Pro_A8$Area  == "Nigeria" | 
                                 Pop_Pro_A8$Area  == "China" | 
                            Pop_Pro_A8$Area  == "United States" | 
                              Pop_Pro_A8$Area  == "India" | 
                            Pop_Pro_A8$Area  == "Germany" | 
                              Pop_Pro_A8$Area  == "Brazil" |
                            Pop_Pro_A8$Area  == "Denmark" | 
                              Pop_Pro_A8$Area  == "Canada"),]
```

```{r}
Pop_Pro_A8 %>% 
  ggplot(aes(x=Year, y=Production, colour = Item)) + 
  stat_summary(fun.y = "mean", geom = "line") +
  facet_wrap(~Area) +
  scale_x_continuous(breaks=seq(1961, 2013, 10)) + 
  labs(x="Year", y="Production (by 1000 tons)", 
  title="Average Amount of Items Produced by Country", 
  color="Item") +
  theme(text = element_text(size=17), axis.text.x = element_text(angle=90, hjust=1))
```

```{r}
Pop_Pro_A8 %>% 
  ggplot(aes(x=Year, y=Production)) + 
  stat_summary(fun.y = "mean", geom = "line", size = 1) +
  facet_wrap(~Item) +
  scale_x_continuous(breaks=seq(1961, 2013, 10)) + 
  labs(x="Year", y="Production (by 1000 tons)", 
  title="Average Amount of Items Produced by Country", 
  color="Item") +
  theme(text = element_text(size=17), axis.text.x = element_text(angle=90, hjust=1))
```

```{r}
Pop_Pro_A8 %>%
  ggplot(aes(x = Area, y = Production, colour = "red")) +
  geom_boxplot(notch=TRUE, outlier.colour="black") +
  labs(x = "Country", y = "Items produced (by 1000 tons)", 
       title = "Items Produced by Country from 1961 to 2013") +
  scale_y_continuous(limits=c(0, 150000)) +
  theme(text = element_text(size=17), axis.text.x = element_text(angle=90, hjust=1), legend.position="none")  
```

```{r}
Pop_Pro_A8_2 <- Pop_Pro_A8 %>%
  group_by(Area, Year, Element, Item)%>%
  summarise(ProByPop = sum(Production/Population), Avg_Production_year = sum(Production)/52)
```

```{r}
Pop_Pro_A8_2 %>%
  group_by(Area)%>%
  ggplot(aes(x = Year, y = ProByPop, colour = Area)) +
  stat_summary(fun.y = "mean", geom = "line", size = 1) +
  scale_x_continuous(breaks=seq(1961, 2013, 10)) +
  facet_wrap(~Element) +
  labs(x = "Year", y = "Amount Produced by Population", 
       title = "Element of Production of Population by Country") +
  theme(text = element_text(size=17), axis.text.x = element_text(angle=90, hjust=1))
```

```{r}
Pop_Pro_A8_2 %>%
  group_by(Item)%>%
  ggplot(aes(x = Year, y = ProByPop, colour = Item)) +
  stat_summary(fun.y = "mean", geom = "line", size = 1) +
  scale_x_continuous(breaks=seq(1961, 2013, 10)) +
  facet_wrap(~Element) +
  labs(x = "Year", y = "Amount Produced by Population", 
       title = "Element of Production of Population by Item") +
  theme(text = element_text(size=17), axis.text.x = element_text(angle=90, hjust=1))
```

#most produced item
```{r}
Pop_Pro_A8_3 <- Pop_Pro_A8 %>%
  group_by(Area, Year)%>%
  mutate(ProByPop = sum(Production, na.rm=T)/sum(Population, na.rm=T), Avg_Production_year = sum(Production)/52)
```

```{r}
Pop_Pro_A8_4 <- Pop_Pro_A8 %>%
  group_by(Item, Year)%>%
  mutate(ProByPop_Item = sum(Production, na.rm=T)/sum(Population, na.rm=T), Avg_Production_year_item = sum(Production)/52)
```

```{r}
Pop_Pro_A8_3 %>%
  group_by(Area)%>%
  ggplot(aes(x = Year, y = Production)) +
  geom_line(aes(x=Year, y=ProByPop, colour = Area), size = 1) + 
  scale_x_continuous(breaks=seq(1961, 2013, 10)) +
  labs(x = "Year", y = "Amount Produced by Year", 
       title = "Production by Population by Year ") +
  theme(text = element_text(size=17), axis.text.x = element_text(angle=90, hjust=1))
```

```{r}
Pop_Pro_A8_3 %>%
  group_by(Area)%>%
  ggplot(aes(x = Year, y = ProByPop)) +
  geom_line(aes(x=Year, y=ProByPop, colour = Area), size = 1) + 
  scale_x_continuous(breaks=seq(1961, 2013, 10)) +
  labs(x = "Year", y = "Amount Produced by Population", 
       title = "Production by Population by Year ") +
  theme(text = element_text(size=17), axis.text.x = element_text(angle=90, hjust=1))
```

```{r}
Pop_Pro_A8_2 %>%
  group_by(Area)%>%
  ggplot(aes(x = Year, y = ProByPop)) +
  stat_summary(fun.y = "mean", geom = "line", color = "red", size = 1) + 
  scale_x_continuous(breaks=seq(1961, 2013, 10)) +
  labs(x = "Year", y = "Average Food Production", 
       title = "Average Food Production by Population by year") +
  theme(text = element_text(size=17), axis.text.x = element_text(angle=90, hjust=1))
```

```{r}
Pop_Pro_A8_4 %>%
  group_by(Area)%>%
  ggplot(aes(x = Year, y = Production, color = Item)) +
  stat_summary(fun.y = "mean", geom = "line", size = 1) + 
  scale_x_continuous(breaks=seq(1961, 2013, 10)) +
  labs(x = "Year", y = "Item Production", 
       title = "Item Production per Year") +
  theme(text = element_text(size=17), axis.text.x = element_text(angle=90, hjust=1)) 

```

```{r}
Pop_Pro_A8_4 %>%
  group_by(Area)%>%
  ggplot(aes(x = Year, y = ProByPop_Item, color = Item)) +
  stat_summary(fun.y = "mean", geom = "line", size = 1) + 
  scale_x_continuous(breaks=seq(1961, 2013, 10)) +
  labs(x = "Year", y = "Item Production", 
       title = "Item Production per Year by Population") +
  theme(text = element_text(size=17), axis.text.x = element_text(angle=90, hjust=1)) 

```

```{r}

pop_noInCh <- Pop_Pro_A8 %>%
    filter(Area != "China")
pop_noInCh <- pop_noInCh %>%
    filter(Area != "India")

Pop_Pro_A8 %>%
  group_by(Area)%>%
  ggplot(aes(x = Year, y = Population, color = Area)) +
  stat_summary(fun.y = "mean", geom = "line", size = 1) + 
  scale_x_continuous(breaks=seq(1961, 2013, 10)) +
  labs(x = "Year", y = "Population", 
       title = "Population by Year") +
  theme(text = element_text(size=17), axis.text.x = element_text(angle=90, hjust=1)) 
```

```{r}
#changing food and feed to 1 and 0
POP_PRO_F = mutate(POP_PRO, Element_0 = ifelse (Element != "Food" & Element != "Feed", 
                                         NA_integer_, ifelse(Element == "Food", 1, 0)))
table(POP_PRO_F$Element_0)
```



##Regressions: Linear
---------------------
```{r}
lin.reg0 <- lm(Production ~ Population + Element_0 + Year + Population:Element_0, POP_PRO_F)
summary(lin.reg0)
```

All variables are shown to be highly significant but the residuals are not working because it says there is a difference in the size of the dataset between residuals and my original data

# ```{r}
# Pop_Prod_Res <- cbind(POP_PRO_F, lin.reg0$residuals)
# 
# Pop_Prod_Res <- Pop_Prod_Res %>%
#   rename(res1 = "lin.reg0$residuals")
# ```
----------------------


##Making Countries and Items into 0 and 1 as well as Element in smaller data set
```{r}
#Is country
Pop_Pro_8_Split = mutate(Pop_Pro_A8, IsChina = ifelse(Area == "China", 1, 0), 
                        IsNigeria = ifelse(Area == "Nigeria", 1, 0), 
                        IsUS = ifelse(Area == "United States", 1, 0), 
                        IsIndia = ifelse(Area == "India", 1, 0), 
                        IsGermany = ifelse(Area == "Germany", 1, 0), 
                        IsBrazil = ifelse(Area == "Brazil", 1, 0), 
                        IsDenmark = ifelse(Area == "Denmark", 1, 0), 
                        IsCanada = ifelse(Area == "Canada", 1, 0))

#Is Item
Pop_Pro_8_Split = mutate(Pop_Pro_8_Split, IsCereals = ifelse(Item == "Cereals - Excluding Beer", 1, 0), 
                        IsMilk = ifelse(Item == "Milk - Excluding Butter", 1, 0), 
                        IsVegetables = ifelse(Item == "Vegetables", 1, 0), 
                        IsRoots = ifelse(Item == "Starchy Roots", 1, 0), 
                        IsMaize = ifelse(Item == "Maize and products", 1, 0), 
                        IsPotatoes = ifelse(Item == "Sweet potatoes", 1, 0), 
                        IsFruits = ifelse(Item == "Fruits - Excluding Wine", 1, 0), 
                        IsRice = ifelse(Item == "Rice (Milled Equivalent)", 1, 0))

#Element Food or Feed 1 or 0
Pop_Pro_8_Split = mutate(Pop_Pro_8_Split, Element_0 = ifelse (Element != "Food" & Element != "Feed", 
                                         NA_integer_, ifelse(Element == "Food", 1, 0)))
table(Pop_Pro_8_Split$Element_0)
```

```{r}
lin_reg1 <- lm(Production ~ Population + Element_0 + Year + IsChina + IsNigeria + IsUS + 
                 IsIndia + IsGermany + IsBrazil + IsDenmark + IsCanada + IsCereals + IsMilk + 
                 IsVegetables + IsRoots + IsMaize + IsPotatoes + IsFruits + IsRice, Pop_Pro_8_Split)
summary(lin_reg1)
```

```{r}
Correlation_data <- Pop_Pro_8_Split[c(5:24)]
cor(Correlation_data)
rm(Correlation_data)
```

```{r}
#ones with issues removed and non significant variables and added in interaction term
lin_reg1.5 <- lm(Production ~ Population + Element_0 + Year + IsChina + IsNigeria + IsUS + 
                 IsIndia + IsCereals + IsVegetables + IsRoots + IsMaize + IsPotatoes + 
                 Year:Element_0, Pop_Pro_8_Split)
summary(lin_reg1.5)
```

```{r}
Pop_Prod_Res1 <- cbind(Pop_Pro_8_Split, lin_reg1.5$residuals, lin_reg1.5$fitted.values) %>%
  rename(fit1 = "lin_reg1.5$fitted.values", res1 = "lin_reg1.5$residuals")
```

```{r}
Pop_Prod_Res1 %>%
  ggplot(aes(res1))+
  geom_histogram(fill = "pink", color = "blue")

qqnorm(Pop_Prod_Res1$res1)

Pop_Prod_Res1 %>%
  ggplot(aes(fit1, res1)) +
  geom_point(color = "darkgreen")
```

The residuals from the Full data set are highly skewed

```{r}
Pop_Pro_8_Split_step <- Pop_Pro_8_Split[c(5:24)]
Pop_Pro_8_Split_step <- na.omit(Pop_Pro_8_Split_step)

#use stepwise
null <- lm(Production~1, data = Pop_Pro_8_Split_step)
full <- lm(Production~., data = Pop_Pro_8_Split_step)
step(null, scope=list(lower=null, upper = full), direction = "forward")
```

```{r}
#run the function the stepwise regression gave 
lin_reg_step <- lm(formula = Production ~ Population + IsCereals + IsUS + Element_0 + 
    IsIndia + IsChina + IsPotatoes + IsVegetables + IsRoots + 
    IsNigeria + IsMaize + IsBrazil, data = Pop_Pro_8_Split_step)
summary(lin_reg_step)

```

```{r}
#run the function the stepwise regression gave but put back in year since that's an important thing
#Remove brazil
lin_reg_stepY <- lm(formula = Production ~ Population + IsCereals + IsUS + Element_0 + 
    IsIndia + IsChina + IsPotatoes + IsVegetables + IsRoots + 
    IsNigeria + IsMaize, data = Pop_Pro_8_Split_step)
summary(lin_reg_stepY)
```

This is the best model. Even if the Rsqaured is not good that makes sense because there are so many data points and this is a subset of the main data because running this regression on the main data is neigh impossible because there are so many different countries and items.


```{r}
Pop_Prod_Res <- cbind(Pop_Pro_8_Split_step, lin_reg_stepY$residuals, lin_reg_stepY$fitted.values) %>%
  rename(fit = "lin_reg_stepY$fitted.values", res2 = "lin_reg_stepY$residuals")
```

```{r}
Pop_Prod_Res %>%
  ggplot(aes(res2))+
  geom_histogram(fill = "pink", color = "blue")

qqnorm(Pop_Prod_Res$res2)

Pop_Prod_Res %>%
  ggplot(aes(fit, res2)) +
  geom_point(color = "mediumspringgreen")
```
The data is still very skewed so trying to run transformations on the output is a good idea. (possibly on inputs too like population)

```{r}
#Transformations sqrt Prod and sq Pop
Pop_Prod_Res2 <- Pop_Pro_8_Split_step %>%
  mutate(sqrtProd = sqrt(Production), sqPop = Population^2)

lin_reg <- lm(formula = sqrtProd ~ sqPop + IsCereals + IsUS + Element_0 + 
    IsIndia + IsChina + IsPotatoes + IsVegetables + IsRoots + 
    IsNigeria + IsMaize, data = Pop_Prod_Res2)
summary(lin_reg)
```
Its not particularily necessary to remove the variables that are not statitically significant because they were significant in the previous model

```{r}
#remove non statistically significant variables
lin_reg4 <- lm(formula = sqrtProd ~ sqPop + IsCereals + IsUS + Element_0 + IsChina + IsPotatoes + IsRoots + 
    IsNigeria, data = Pop_Prod_Res2)
summary(lin_reg4)
```
the Rsquared dropped slightly because of losing 2 variables but not enough to worry about

###Res plots for sqrtProd
```{r}
Pop_Prod_Res2 <- cbind(Pop_Pro_8_Split_step, lin_reg4$residuals, lin_reg4$fitted.values) %>%
  rename(fit.sqrtProd = "lin_reg4$fitted.values", res.sqrtProd = "lin_reg4$residuals")

Pop_Prod_Res2 %>%
  ggplot(aes(res.sqrtProd))+
  geom_histogram(color = "yellow", fill = "lightblue")

qqnorm(Pop_Prod_Res2$res.sqrtProd)

Pop_Prod_Res2 %>%
  ggplot(aes(fit.sqrtProd, res.sqrtProd)) +
  geom_jitter(color = "orchid1")
```

###Res plots for the removed values in sqrt
```{r}
Pop_Prod_Res2 <- cbind(Pop_Pro_8_Split, lin_reg4$residuals)

Pop_Prod_Res2 <- Pop_Prod_Res2 %>%
  rename(res4 = "lin_reg4$residuals")

Pop_Prod_Res2 %>%
  ggplot(aes(res4))+
  geom_histogram(color = "yellow", fill = "lightblue")

qqnorm(Pop_Prod_Res2$res4)

Pop_Prod_Res %>%
  ggplot(aes(fit, res2)) +
  geom_point(color = "mediumspringgreen")
```


```{r}
#ncvTest
#ncvTest(lin_reg4)

#Shapiro Test
#shapiro.test(lin_reg4$residuals) 
```

#run regression on subset and single variable
```{r}
lin.reg0.5 <- lm(Production ~ Population, Pop_Pro_8_Split)
summary(lin.reg0.5)
```

```{r}
Pop_Prod_Res <- cbind(Pop_Pro_8_Split, lin.reg0.5$residuals)

Pop_Prod_Res <- Pop_Prod_Res %>%
  rename(res1 = "lin.reg0.5$residuals")
```

```{r}
Pop_Prod_Res %>%
  ggplot(aes(res1))+
  geom_histogram()

qqnorm(Pop_Prod_Res$res1)
```

```{r}
Pop_Pro_8_Split <- Pop_Pro_8_Split%>%
  mutate(sqPop = Population^2, logPop = log(Population), sqrtPop = sqrt(Population))

#lin.reg.sqPop <- lm(Production ~ sqPop, Pop_Pro_8_Split)
#summary(lin.reg.sqPop)

#lin.reg.logPop <- lm(Production ~ logPop, Pop_Pro_8_Split)
#summary(lin.reg.logPop)

lin.reg.sqrtPop <- lm(Production ~ sqrtPop, Pop_Pro_8_Split)
summary(lin.reg.sqrtPop)
```

###Res plots for sqrtPop
```{r}
Pop_Prod_Res <- cbind(Pop_Pro_8_Split, lin.reg.sqrtPop$residuals)

Pop_Prod_Res <- Pop_Prod_Res %>%
  rename(resid.sqrtPop = "lin.reg.sqrtPop$residuals")

Pop_Prod_Res %>%
  ggplot(aes(resid.sqrtPop))+
  geom_histogram()

qqnorm(Pop_Prod_Res$resid.sqrtPop)
```

All of the transformations for Population did not work so in an attempt to make the residuals better I will add more variables to the regression itself



```{r}
#Production vs Residuals
Pop_Prod_Res %>%
  ggplot(aes(Population, Production)) +
  geom_point(colour = "purple3") +
  geom_smooth(method = "lm")
```

This data suffers highly from heteroskedacity as well as there appears to be a weird chunk of the data missing


```{r}
Pop_Prod_Res %>%
  ggplot(aes(Year, Production)) +
  geom_point(colour = "olivedrab4") +
  geom_smooth(method = "lm")
```

```{r}
Pop_Prod_Res %>%
  ggplot(aes(Element_0, Production)) +
  geom_point(colour = "hotpink2") +
  geom_smooth(method = "lm")
```

```{r}

```



